Strong lensing selection effects

### 2022-06-26 paper/seleff.tex
first plot

@@

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{axisymm_pl_crosssect.eps}
\caption{
Strong lensing cross-section of an axisymmetric power-law lens and a point source, as a function of the power-law slope $\gamma$.
The system is defined as a strong lens if at least two images are detected.
Different lines correspond to the difference $\Delta m$ between the source magnitude and the survey detection limit for a point source.
The dashed line marks the cross-section in the case in which at least two images are formed, regardless of their magnification.
}
\end{figure}

@@

Discuss.
